Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries

### 2021-06-17 paper/tex/sections/introduction.tex
remove gaia mentions

We build upon previous efforts but with several important improvements. We explore the effect of varying binary physics assumptions by repeating our analysis for 15 different models and comparing the effect on the detection rate and distributions of source parameters. We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest GAIA and APOGEE surveys \citep{GaiaCollaboration+2016,Majewski+2017,Frankel+2018}. We provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission. Moreover, our binary population synthesis simulation is the most extensive of its kind to date, with 750 million simulated massive binaries (one million binaries for each of 50 metallicity bins and 15 physics variations) evolved to produce the DCO populations used in this work \citep{Broekgaarden+2021}. We find that this large number of simulations is important to reduce the sampling noise. In addition, we use the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to further reduce this sampling noise.

>>>>

We build upon previous efforts but with several important improvements. We explore the effect of varying binary physics assumptions by repeating our analysis for 15 different models and comparing the effect on the detection rate and distributions of source parameters. We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}. We provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission. Moreover, our binary population synthesis simulation is the most extensive of its kind to date, with 750 million simulated massive binaries (one million binaries for each of 50 metallicity bins and 15 physics variations) evolved to produce the DCO populations used in this work \citep{Broekgaarden+2021}. We find that this large number of simulations is important to reduce the sampling noise. In addition, we use the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to further reduce this sampling noise.
